Geometric variational problems

### 2020-11-13 NSF2020/Description/broaderimpacts.tex
broader impacts edited

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
The proposed research will have an immediate impact on undergraduate and
graduate education. At the undergraduate level, the project will include
and support undergraduate researchers from Fordham University. The
supported summer researchers will gain valuable first-hand
interdisciplinary experience in mathematical fluid modeling and
computation. We will incorporate research into teaching, especially in
differential equation and programming courses. PI YNY will work on
simple modeling of self-assembly problems with both undergraduate and
high school students from Newark Science Park High School. PI YNY has a
track record of working with local high school students for their
research projects before they apply for colleges. PI BQ will work with
undergraduate and high school students through the Undergraduate
Research Opportunity Program and Young Scholar's Program as he has done
in the past.

@@

The PIs will capitalize on the synergy between both FSU's doctoral program in Scientific Computing and NJIT's doctoral programs
in Mathematical Sciences and Fordham's undergraduate focus in the
Department of Mathematics. Promising, young undergraduate scientists
from the Bronx community will find a natural pipeline into graduate
studies by working directly or indirectly on this project. On the
graduate-level education, PI YNY expects to train and support a PhD
student for two more years. PI BQ will advise a postdoctoral fellow for
two years. The PIs will foster vertical integration between the senior
personnel, their collaborators, postdocs, doctoral, and Bachelor
students, enhancing the learning environment.

@@

\section{Intellectual Merit}
A central theme of the project is the mathematical development and
analysis of the physical model for interaction between many amphiphilic
particles. The model formulates the interaction potential through a
screened Laplace equation boundary value problem possessing the physical
properties like non-additivity and decay of realistic hydrophobic
attraction. Colloidal systems collectively self-assemble into bilayer
morphologies, and we analyze the elastic properties of these amphiphilic
particle ensembles. This allows us to interpret the Helfrich free energy
in terms of hydrophobic interactions and specific molecular
characteristics. We extend the capabilities of the boundary integral
equation and time stepping methods to stably perform large particle
number simulations in three dimensions. Results from these computations
will be used to compare collective amphiphilic against experiments, and
study the optimal design of three-dimensional functional materials.

>>>>

\subsection{Educational Impacts}
\label{subsec:Educational_plans}
The proposed research will have an immediate impact on undergraduate and
graduate education. At the undergraduate level, the project will include
and support undergraduate researchers from Fordham University. The
supported summer researchers will gain valuable first-hand
interdisciplinary experience in mathematical modeling and computation.
We will incorporate research into teaching, especially in differential
equation and programming courses. PI YNY will work on simple modeling of
self-assembly problems with both undergraduate and high school students
from Newark Science Park High School. PI YNY has a track record of
working with local high school students for their research projects
before they apply for colleges. PI BQ will work with undergraduate and
high school students through the Undergraduate Research Opportunity
Program and Young Scholar's Program as he has done in the past.

@@

The PIs will capitalize on the synergy between both FSU's doctoral
program in Scientific Computing, NJIT's doctoral program in Mathematical
Sciences, and Fordham's undergraduate focus in the Department of
Mathematics. Promising, young undergraduate scientists from the Bronx
community will find a natural pipeline into graduate studies by working
directly or indirectly on this project. At the graduate-level, PI YNY
expects to train and support a PhD student for two more years. PI BQ
will advise a postdoctoral fellow for two years. The PIs will foster
vertical integration between the senior personnel, their collaborators,
postdocs, doctoral, and Bachelor students, enhancing the learning
environment.

@@

\section{Intellectual Merit}
A central theme of the project is the mathematical development and
analysis of the physical model for interaction between many amphiphilic
particles. The model formulates the interaction potential through a
screened Laplace equation boundary value problem possessing the physical
properties like non-additivity and decay of realistic hydrophobic
attraction. Colloidal systems collectively self-assemble into bilayer
morphologies, and we analyze the elastic properties of these amphiphilic
particle ensembles. This allows us to interpret the Helfrich free energy
in terms of hydrophobic interactions and specific molecular
characteristics. We extend the capabilities of the boundary integral
equation and time stepping methods to stably perform large particle
number simulations in three dimensions. Results from these computations
will be used to compare collective amphiphilic against experiments and
to study the optimal design of three-dimensional functional materials.
